---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fossil

<!-- badges: start -->
<!-- badges: end -->

The goal of **fossil** is to help the user gain information about the fossil fuels mainly *oil*, *natural gas* and *coal*. We can get information about the production, consumption , total reserves of the above mentioned fossil fuels for different countries and of different years. The package also has functions that lets the used find the average production, and also lets the user find about the top 10 producers of a fossil fuel for a particular year. The package also contains functions to launch the shiny apps which helps the user interactively use the data.

## Installation

You can install the development version of fossil from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("etc5523-2022/rpkg-kvatsal2000")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(fossil)
# To find the average oil production of 2002:
oil_prod(2002)
```
```{r example2}

# To find the top 10 oil producers of 2002
top_oil(2002)

```


