---
title: "R Package FOSSIL"
author: "Kumar Vatsal"
format:
  revealjs:
    theme: sky
    incremental: true
    scrollable: true
    transition: convex
    background-transition: convex
---

## INTRODUCTION 
This package can help the user gain information about the fossil fuels mainly *oil*, *natural gas* and *coal*. We can get information about the production, consumption , total reserves of the above mentioned fossil fuels for different countries and of different years. The package also has functions that lets the used find the average production, and also lets the user find about the top 10 producers of a fossil fuel for a particular year. The package also contains functions to launch the shiny apps which helps the user interactively use the data.

## DATA



The datasets used to create this package are

::: {.incremental}

-   **resources_data**

This dataset contains information about fossil fuel production, consumption, population of the country,year and the total reserves of natural resources of different countries from 1973 to 2021. The data set can be found [HERE](https://ourworldindata.org/explorers/natural-resources) The user can use *resoursecs_data()* function to access the dataset.

-   **resource_data2**

This data is a subset of the above mentioned data and has some columns pivited to help create the shiny app. The user can use *resource_data2()* function to access the dataset.

:::

## Functions in the package

The functions that are available in this package are as follows:

::: {.incremental}

- resources_data() : This function can be called to display the main dataset that is used to create this package.

- This function is used to display the modified version of the 
dataset that is used to create the shiny app.

:::

---

::: {.incremental}

- oil_prod : This function takes year as an input and returns the average oil 
produced in that year by all the countries combined. 

```{r}
#| echo: true
fossil::oil_prod(2000)
```

- gas_prod : This function takes year as an input and returns the average natural
gas produced in that year by all the countries combined.

```{r}
#| echo: true
fossil::gas_prod(2000)
```

- coal_prod : This function takes year as an input and returns the average coal 
produced in that year by all the countries combined.

```{r}
#| echo: true
fossil::coal_prod(2000)
```

:::

---

::: {.incremental}

- top_oil : This function takes year as an input and returns a table showing
the top 10 oil producers of that year and the total oil produced by them in that 
year.

```{r}
#| echo: true
fossil::top_oil(2000)
```


- top_gas : This function takes year as an input and returns a table showing
the top 10 natural gas producers of that year and the total natural gas produced by them in that year.

```{r}
#| echo: true
fossil::top_gas(2000)
```


- top_coal : This function takes year as an input and returns a table showing
the top 10 coal producers of that year and the total coal produced by them in that 
year.

```{r}
#| echo: true
fossil::top_coal(2000)
```

:::

---

- run_app : This function can be used to launch the shiny app which lets the user
interactively use the data.

*run_app()*

- shiny_pa : This function launches a parametarized version of the shiny app in 
which we enter the natural resource whose data we want to choose and then when the 
shiny app is launched, the user can select the country using the drop down menu and can see the production trend of the given fossil fuel through the years.

*shiny_pa(2000)*

## DOCUMENTATION

The package documentation and full info can be found [https://etc5523-2022.github.io/rpkg-kvatsal2000/](https://etc5523-2022.github.io/rpkg-kvatsal2000/)


## THANK YOU
